Reducing Acceptance Marks in Emerson-Lei Automata by QBF-solving

### 2022-04-26 paper/table-data.tex

\begin{tabular}{ccccccc}                                                        
\toprule                                                                        
automata set & level & marks & reduction [\%] & time [s] & \makecell{solver \\ response} & \makecell{solver \\ timeout} \\

\midrule
\multirow{4}{*}{\makecell{\texttt{ltl2dela}\\129 automata\\523 acc.~marks}}
&
level 1 &
387 & 26.0 & 736.5 & 111 & 18
\\
&
level 2 &
395 & 24.5 & 954.6 & 108 & 21
\\
&
level 3 &
397 & 24.1 & 7089.0 & 103 & 26
\\
&
multi &
379 & 27.5 & 9128.6 & 105 & 24
\\
\midrule
\multirow{4}{*}{\makecell{\texttt{ltl2dgra}\\234 automata\\882 acc.~marks}}
&
level 1 &
552 & 37.4 & 718.7 & 220 & 14
\\
&
level 2 &
569 & 35.5 & 866.0 & 216 & 18
\\
&
level 3 &
561 & 36.4 & 1148.5 & 213 & 21
\\
&
multi &
543 & 38.4 & 2310.9 & 211 & 23
\\
\midrule
\multirow{4}{*}{\makecell{\texttt{ltl2tgba}\\70 automata\\198 acc.~marks}}
&
level 1 &
198 & 0.0 & 34.6 & 70 & 0
\\
&
level 2 &
198 & 0.0 & 66.4 & 70 & 0
\\
&
level 3 &
189 & 4.5 & 1256.5 & 63 & 7
\\
&
multi &
189 & 4.5 & 1288.2 & 64 & 6
\\
\midrule
\multirow{4}{*}{\makecell{\texttt{ltl3tela}\\91 automata\\348 acc.~marks}}
&
level 1 &
332 & 4.6 & 454.3 & 79 & 12
\\
&
level 2 &
334 & 4.0 & 537.8 & 76 & 15
\\
&
level 3 &
326 & 6.3 & 680.7 & 72 & 19
\\
&
multi &
323 & 7.2 & 1548.2 & 73 & 18
\\

>>>>

\begin{tabular}{ccrrrr}
\toprule                                                                        
automata set & level & marks & reduction [\%] & time [s] & \makecell{solver \\[-1ex] timeout} \\

\midrule
\multirow{4}{*}{\makecell{\texttt{ltl2dela}\\129 automata\\523 acc.~marks}}
&
level 1 &
387 & 26.0 & 755.4 &  18
\\
&
level 2 &
390 & 25.4 & 1024.5 &  20
\\
&
level 3 &
393 & 24.9 & 7273.3 &  25
\\
&
multi &
371 & 29.1 & 9111.4 &  21
\\
\midrule
\multirow{4}{*}{\makecell{\texttt{ltl2dgra}\\234 automata\\882 acc.~marks}}
&
level 1 &
552 & 37.4 & 738.7 & 14
\\
&
level 2 &
569 & 35.5 & 907.3 &  18
\\
&
level 3 &
561 & 36.4 & 1163.4 &  21
\\
&
multi &
542 & 38.5 & 2320.7 &  21
\\
\midrule
\multirow{4}{*}{\makecell{\texttt{ltl2tgba}\\70 automata\\198 acc.~marks}}
&
level 1 &
198 & 0.0 & 49.3 &  0
\\
&
level 2 &
198 & 0.0 & 78.9 & 0
\\
&
level 3 &
189 & 4.5 & 1222.8 & 7
\\
&
multi &
189 & 4.5 & 1259.1 & 6
\\
\midrule
\multirow{4}{*}{\makecell{\texttt{ltl3tela}\\91 automata\\348 acc.~marks}}
&
level 1 &
332 & 4.6 & 465.9 &  12
\\
&
level 2 &
334 & 4.0 & 553.9 &  15
\\
&
level 3 &
326 & 6.3 & 691.8 &  18
\\
&
multi &
323 & 7.2 & 1545.9 & 18
\\
